Abstract Data Type Inference

### 2015-03-24 histories.tex
The last TODO.

A matching scheme $\tup{M,R}$ is \emph{faithful} to a set $E$ of executions
when $e \in E$ if{f} $e' \in E$ for any two executions $e$ and $e'$ such that
$H(e,M,R) = H(e',M,R)$. A set of executions $E$ is \emph{data
independent}\footnote{TODO NOTE THAT THIS IS NOT THE STANDARD DEFINITION…} when
there exists a faithful matching scheme. By definition, our abstraction of
executions into histories incurs no loss of precision for data-independent
execution sets.

>>>>

A matching scheme $\tup{M,R}$ is \emph{faithful} to a set $E$ of executions
when $e \in E$ if{f} $e' \in E$ for any two executions $e$ and $e'$ such that
$H(e,M,R) = H(e',M,R)$. A set of executions $E$ is \emph{data
independent}\footnote{Our definition of \emph{data independence} formalizes an
existing informal notion, which stipulates that the implementation generating a
set of executions does not predicate its actions on the data values passed as
method arguments.} when there exists a faithful matching scheme. By definition,
our abstraction of executions into histories incurs no loss of precision for
data-independent execution sets.
